Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-13 paper.qmd
Changed color palattes

error_plot_pbmc <- ggplot(error_df, 
                              aes(x = b_non_empty, 
                                  y = log(error), 
                                  group = type, 
                                  colour = type)) + 
  geom_point() +
  geom_line() + 
  geom_vline(xintercept = 137, linetype="solid", 
             color = "black", size=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99',
                              '#e31a1c','#fdbf6f','#ff7f00','#cab2d6','#6a3d9a', 
                              '#b15928', '#ffff99')) +
  ylab("log(absolute error)") +
  xlab("number of non-empty bins")

@@

benchmark_pbmc <- 0.1

>>>>

error_plot_pbmc <- ggplot(error_df, 
                              aes(x = b_non_empty, 
                                  y = log(error), 
                                  group = type, 
                                  colour = type)) + 
  geom_point() +
  geom_line() + 
  geom_vline(xintercept = 137, linetype="solid", 
             color = "black", size=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#984ea3',
                              '#ff7f00','#a6cee3','#a65628','#f781bf')) +
  ylab("log(absolute error)") +
  xlab("number of non-empty bins")

@@

## To find the benchmark value
benchmark_pbmc <- find_lg_benchmark(
  distance_edges = distance_pbmc,
  distance_col = "distance")
benchmark_pbmc <- 0.1
